Something about Performance, 2D Component of NEMO. (TBC)

### 2016-08-19 nemolite2d_perf.tex
nemolite2d-perf: added an abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

>>>>

\begin{abstract}

We present an approach which we call \psykal\ that aims to achieve
portable performance for parallel, finite-difference Ocean models.  In
\psykal\ the code related to the underlying science is formally
separated from code related to parallelisation and single-core
optimisations. This separation of concerns allows scientists to code
their science independently of the underlying hardware architecture
and for optimisation specialists to be able to tailor the code for a
particular machine independently of the science code. We have taken
the free-surface part of the NEMO ocean model and created a new,
shallow-water model named NEMOLite2D. In doing this we have a code
which is of a manageable size and yet which incorporates elements of
full ocean models (input/output, boundary conditions, \textit{etc.}).
We have then manually constructed a \psykal\ version of this code and
investigated the transformations that must be applied to the
middle/PSy layer in order to achieve good performance, both serial and
parallel. We have produced versions of the PSy layer parallelised with
both OpenMP and OpenACC; in both cases we were able to leave the
natural-science parts of the code unchanged while achieving good
performance on both multi-core CPUs and GPUs. In quantifying whether
or not the obtained performance is `good' we also consider the
limitations of the basic roofline model and attempt to improve on it
by generating kernel-specific CPU ceilings.

\end{abstract}
